DOpElib:\\ Differential Equations and Optimization Environment

### 2014-10-14 Examples/Documentation/examples.tex

  Change to the \texttt{Test} sub-directory. And then modify the
  test-script to contain the new name of the executable.
  Assuming you want to use Emacs, open the file \texttt{test.sh}
\begin{verbatim}
PDE/StatPDE/Example1/Test> emacs test.sh
\end{verbatim}
where, in our example you find two times the lines
\begin{verbatim}
echo "Running Program ../../../../../bin/DOpE-PDE-StatPDE-Example1-2d-2d test.prm"
(../../../../../bin/DOpE-PDE-StatPDE-Example1-2d-2d test.prm 2>&1) > /dev/null
\end{verbatim} 
if you made a copy of an other example the part \texttt{DOpE-PDE-StatPDE-Example1-2d-2d}
may differ. These lines need to be replaced with the new name of the 
executable, i.e., for our given example
\begin{verbatim}
echo "Running Program ../../../../../bin/MyWonderfulFirstExample test.prm"
(../../../../../bin/MyWonderfulFirstExample test.prm 2>&1) > /dev/null
\end{verbatim}

@@

  To do so, change to the \texttt{Test} sub-directory and run the test:
\begin{verbatim}
./test Test
\end{verbatim}
  Note that this should fail, otherwise you have not changed anything in the program, 
  or forgot part 3) of this description.

@@

  Once your satisfied with what you see in the log-file \texttt{dope.log} you need to store 
  that information using
\begin{verbatim}
./test Store
\end{verbatim}
\end{enumerate}

>>>>

  Change to the \texttt{Test} sub-directory. And then modify the
  test-script to contain the new name of the executable.
  Assuming you want to use Emacs, open the file \texttt{test.sh}
\begin{verbatim}
PDE/StatPDE/Example1/Test> emacs test.sh
\end{verbatim}
where, in our example you find the line
\begin{verbatim}
PROGRAM=../../../../../bin/DOpE-PDE-StatPDE-Example1-2d-2d
\end{verbatim} 
if you made a copy of an other example the part \texttt{DOpE-PDE-StatPDE-Example1-2d-2d}
may differ. These lines need to be replaced with the new name of the 
executable, i.e., for our given example
\begin{verbatim}
PROGRAM=../../../../../bin/MyWonderfulFirstExample
\end{verbatim}

@@

  To do so, change to the \texttt{Test} sub-directory and run the test:
\begin{verbatim}
./test.sh Test
\end{verbatim}
  Note that this should fail, otherwise you have not changed anything in the program, 
  or forgot part 3) of this description.

@@

  Once your satisfied with what you see in the log-file \texttt{dope.log} you need to store 
  that information using
\begin{verbatim}
./test.sh Store
\end{verbatim}
\end{enumerate}
